MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
added forwarding section

\subsection{Forwarding}
hidclient \cite{hidclient}
\subsection{Keylogging}
We used python script based on findings of \cite{chopper}

@@

\section{Mitigation}
We are proposing three countermeasures to prevent against Man in the Middle attacks on Bluetooth keyboards.

\begin{enumerate}
\item Stay out of discoverable mode as much as possible. This way any attacker would need special hardware to perform any kind of fancy attack and take much longer to actually find the keyboards Bluetooth address.
\item Keyboards should require 
\item Pair with keyboard and victim
\end{enumerate}

No disco mode
Keyboards should force pins to be used, more sensitive than keyboards
Bluetooth managers should be smarter

\section{Future Work}

\section{Conclusions}

>>>>

\subsection{Forwarding}
Although the attacker has now positioned him or herself between the keyboard and the victim PC, the attacker must effectively forward the keystrokes coming from the keyboard to the victim PC, otherwise the jig will be up.   
Theoretically, it's possible to capture the Bluetooth packets from the keyboard, alter the source address to be the attacker's PC Bluetooth address and then forward the packets using C. However, we were unable to parse the Bluetooth packets because of the implementation differences in libpcap between Bluetooth and Ethernet traffic.

We were able to find a work-around considering that our attacker PC is simply emulating a keyboard; therefore, we looked for HID clients that mimic keyboards and use Bluetooth. We found an Linux tool called hidclient \cite{hidclient} which can essentially forward from any input device on the attacker PC.

Hidclient allows the user to forward from any input device the user specifies and that the computer recognizes as a valid input. Since the victim's Bluetooth keyboard is connected to the attacker already, hidclient recognizes the keyboard as an input source. This means the attacker's keyboard is free for typing and will not appear on the victim's screen. The keystrokes are forwarded on to the victim with minimal delay.

\subsection{Keylogging}
We used python script based on findings of \cite{chopper}

@@

\section{Mitigation}
\section{Future Work}
\section{Conclusions}
